---
title: "Challenge 2: Spicing things up with ggplot2"
author: "Eden Schott"
format: html
editor: source
embed-resources: true
code-tools: true
self-contained: true
echo: true
execute: 
  error: false
  messages: false
---

For this week's Challenge, you will have three different options to explore.
I've arranged these options in terms of their "spiciness," or the difficulty of 
completing the task. **You are only required to complete one task, but if you are interested in exploring more than one, feel free!**

This is a great place to let your creativity show! Make sure to indicate what
additional touches you added, and provide any online references you used.

# Getting Set-up 

I created a setup code chunk to load the packages and read in the
`surveys.csv` data file exactly how I did in Lab 2.

```{r}
#| label: setup

library(tidyverse)
surveys <- read_csv("data/surveys.csv")
```

Finally, I created another code chunk and pasted in my code from Question 14 or Question 15 in Lab 2 -- we will be modifying the box plot of weights by species!

```{r}
#| label: boxplot

ggplot(data = surveys,
       mapping = aes(x = weight,
                     y = species,
                     colour = species)) +
  geom_boxplot(outliers = FALSE) + 
  geom_jitter(alpha = .05) +
  labs(x = "Weight",
       y = "Species",
       title = "Distribution of Weight within Each Species")
```

# Medium: Ridge Plots

In Lab 2, you used side-by-side **boxplots** to visualize the distribution of 
weight within each species of rodent. 

A "superior" alternative is the density plot.

> **For this challenge I changed my boxplots to ridge plots and installed the `ggridges` package.**

```{r}
#| label: ridges-package

library(ggridges)
```

```{r}
#| label: density-plot

ggplot(data = surveys,
       mapping = aes(x = weight,
                     y = species,
                     colour = species)) +
  geom_density_ridges() +
  labs(x = "Weight",
       y = "Species",
       title = "Distribution of Weight within Each Species")
```

# Spicy: Exploring Color Themes


### Manual Specification

> **In this challenge I modified the boxplots I created Lab 2. First, I colored the boxplots based on the variable `genus`. Next, I changed the colors used for `genus` using manual color specification.**

```{r}
#| label: color-boxplot

#my custom color vector
eden_palette <- c("#58a81d", "#ca94f5", "#1d9ca8", "#a8741d", "#e663b1", "#e6cc63", "#b9282b", "#6c63e6")

ggplot(data = surveys,
       mapping = aes(x = weight,
                     y = species,
                     colour = genus)) +
  geom_boxplot(outliers = FALSE) + 
  geom_jitter(alpha = .05) +
  labs(x = "Weight",
       y = "Species",
       colour = "Genus",
       title = "Distribution of Weight within Each Species") +
  scale_color_manual(values = eden_palette)
```



# Challenge 2 Submission

Once you have completed your challenge(s) you should upload your rendered HTML file to Canvas.

Your Challenge 2 file **must** be separate from your Lab 2 file. Yes, some of the code for the Challenge is the same as Lab 2 -- you can copy and paste this code into a **new** Quarto file. Your Challenge 2 submission should only included code necessary for completing the Challenge, nothing else.

Similar to Lab 2, you should submit **only** your HTML file. Your HTML file is required to have the following specifications in the YAML options (at the top of your document):

-   have the plots embedded (`embed-resources: true`)
-   include your source code (`code-tools: true`)
-   include all your code and output (`echo: true`)

**If any of the options are not included, your assignment will receive an "Incomplete" and you will be required to submit a revision.**

In addition, your document should not have any warnings or messages output in your HTML document. **If your HTML contains warnings or messages, you will receive an "Incomplete" for document formatting and you will be required to submit a revision.**

